---
title: "CEI's fish abundance"
author: "Luis Malpica"
date: "Jul, 2017"
output: 
  html_document:
    code_folding: hide
---
#Code to sort, plot & analyze CEI's fish abundance
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
#code_folding: hide
```

Data has already been cleaned and sorted, the rest of the code to get to these point was very dirty. Please let me know if you would like to also see that part. These data tables contain average density values per site (AveSpm2) for 2012 and 2013 indicating wether lionfish were removed (1) or not (2), you can disregard the SumSpm2 column, the rest of the column names should be self explanatory.

```{r}
#Load and manipulate data
library(lme4)
library(tidyverse)
library(arm)
library(sjPlot)
library(sjmisc)
library(rstanarm)

#custom theme for sjp plots
sjp.setTheme(base = theme_classic(), 
             legend.title.face = "italic", # title font face
             legend.inside = TRUE,         # legend inside plot
             legend.color = "grey50",      # legend label color
             legend.pos = "bottom right",  # legend position inside plot
             axis.title.size = 1,
             axis.textsize = 1,
             legend.size = 1,
             legend.title.size = 1,
             geom.label.size = 3)

#Load data
LFtar <- read.table("data/LFtar.csv",sep=",", header=T)
comptar <- read.table("data/comptar.csv",sep=",", header=T)
nopredtar <- read.table("data/nopredtar.csv",sep=",", header=T)
smallstar <- read.table("data/smallstar.csv",sep=",", header=T)

#I use these following lines to log densities (AveSpm2)
fish=list(LFtar,comptar,nopredtar,smallstar)
#log_fish <- lapply(fish,function(x)dplyr::mutate(x, log_AveSpm2 = arm::rescale(log(AveSpm2)))) #not used
log_fish <- lapply(fish,function(x)dplyr::mutate(x, log_AveSpm2 = (log(AveSpm2))))
log_fish <- lapply(log_fish, transform, DateCode = as.factor(DateCode), Site = as.character(Site),
                                        RemovTreat = as.factor(RemovTreat))

invasivecomp <- as.data.frame(log_fish[[1]])
nativecomp <- as.data.frame(log_fish[[2]])
allfishsps <- as.data.frame(log_fish[[3]])
preyfishsps <- as.data.frame(log_fish[[4]])

```

```{r}
#Simplified run of Mixed effect model for Reef fish densities (lionfish, native predators, all community, and prey only)
m_LF <- lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = invasivecomp) # exercise
m_natcomp <- lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = nativecomp) # exercise
m_allsps <- lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = allfishsps) # exercise
m_preysps <- lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = preyfishsps) # exercise

arm::display(m_LF)
arm::display(m_natcomp)
arm::display(m_allsps)
arm::display(m_preysps)

#Model coeff plots with sjp.lmer
sjp.lmer(m_LF, type = "fe", axis.lim = c(-2.4, 1.2))
#ggsave("graphs/LF_lmm.pdf", width = 5, height = 4, useDingbats=FALSE)
sjp.lmer(m_natcomp, type = "fe", axis.lim = c(-2.4, 1.2))
#ggsave("graphs/Comp_lmm.pdf", width = 5, height = 4, useDingbats=FALSE)
sjp.lmer(m_allsps, type = "fe", axis.lim = c(-2.4, 1.2))
#ggsave("graphs/allsps_lmm.pdf", width = 5, height = 4, useDingbats=FALSE)
sjp.lmer(m_preysps, type = "fe", axis.lim = c(-2.4, 1.2))
#ggsave("graphs/preysps_lmm.pdf", width = 5, height = 4, useDingbats=FALSE)

#Bayesian version of models with stan_lmer
mb_LF <- stan_lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = invasivecomp) # exercise
mb_natcomp <- stan_lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = nativecomp) # exercise
mb_allsps <- stan_lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = allfishsps) # exercise
mb_preysps <- stan_lmer(log_AveSpm2 ~ RemovTreat + DateCode + (1 | Site), data = preyfishsps) # exercise

summary(mb_LF)
summary(mb_natcomp)
summary(mb_allsps)
summary(mb_preysps)

plot(mb_LF)
plot(mb_natcomp)
plot(mb_allsps)
plot(mb_preysps)

```
